On The Impact of Atoms of Confusion in JavaScript Code

### 2020-11-12 1_Introduction.tex
additional review on sections 1, 2
add a code snippet to make the notion of atoms-of-confusion clearer

Our research aims to help practitioners identify potentially confusing snippets of code, so that
developers could replace them with clearer code.
To achieve that, we investigate {\color{red}XYZ} JavaScript idioms that
might compromize program understanding. These idioms correspond to a set of candidates for \emph{atoms of confusion} in
JavaScript---that is, small
pieces of code that hinder developers' understanding of the source code of a program
for which there are functionally equivalent alternatives that are easier
to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}. \castor{I think it would be really nice to have an example here. Maybe even a figure with a left-hand and a right-hand side. What do you say? If yes, I
'd go for post increment or assignment as value. If not a figure, the text could be as follow: An example of atom of confusion identified by previous work~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} is the use \texttt{if} statements without the accompanying curly braces. The alternative, in this case, is simply to always use the curly braces.}
Among the atoms in this work, X are shared between JavaScript and \clang/\cpplang (e.g., pre/post-increment), while Y others are specific to JavaScript, e.g., the atom Assignment as Value.
Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17} has
already explored the impact of atoms of confusion on program understanding,
and confirmed they negatively impact source code understandability.
However, they were constrained to statically typed languages (e.g., C and C++).
To the best of our knowledge, we are the first to explore atoms of confusion
in the context of a dynamically typed language (JavaScript).\castor{Review the number of atoms, X, and Y.}

>>>>

Our research aims to help practitioners identify potentially confusing snippets of code, so that
developers could replace them with clearer code.
To achieve that, we investigate {\color{red}XYZ} JavaScript idioms that
might compromise program understanding. These idioms correspond to a set of candidates for \emph{atoms of confusion} in
JavaScript---that is, small
pieces of code that hinder developers' understanding of the source code of a program
for which there are functionally equivalent alternatives that are easier
to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}. For instance, consider
the pair of code snippets in Listing~\ref{fig:lst01} (adapted from \textsc{NervJS/taro}
for presentation purpose only). The code in the left of the figure contains two atoms of confusion discussed in a previous work~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic as Control Flow} and \emph{Post-increment}. On the right we present a cleaned version of the code, that is, without atoms of confusion. According to
Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} removing
the atom \emph{Logic as Control Flow} and \emph{Post-increment} improves the accuracy of
program understanding tasks in  41\% and 34\%, respectively.

Among the atoms in this work, X are shared between JavaScript and \clang/\cpplang (e.g., pre/post-increment), while Y others are specific to JavaScript, e.g., the atom Assignment as Value.
Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17} has
already explored the impact of atoms of confusion on program understanding,
and confirmed they negatively impact source code understandability.
However, they were constrained to statically typed languages (e.g., \clang and \cpplang).
To the best of our knowledge, we are the first to explore atoms of confusion
in the context of a dynamically typed language (JavaScript).\castor{Review the number of atoms, X, and Y.}

\begin{figure*}
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\label{fig:lst01}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 in the left hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. In the right hand side, we present the alternative code without atoms of confusion. We could simplify the code on the left even more, by replacing the \texttt{reduce} recursive pattern by a functional composition between the \texttt{filter} and
\texttt{length} patterns (e.g., \texttt{res = properties.filter(p => p).length}).}
\end{figure*}
